\begin{frame}
\frametitle{Free Books}
\begin{itemize}
\item {\bf The Elements of Statistical Learning: Data Mining, Inference, and Prediction}
      Trevor Hastie, Robert Tibshirani, Jerome Fried(2009)
      \url{http://statweb.stanford.edu/~tibs/ElemStatLearn/}
\item {\bf An Introduction to Statistical Learning with Applications in R}
      Gareth James, Daniela Witten, Trevor Hastie and Robert Tibshirani (2013)
      \url{http://www-bcf.usc.edu/\%7Egareth/ISL/}
\item {\bf Introduction to Machine Learning}
      Amnon Shashua (2008)
      \url{http://arxiv.org/pdf/0904.3664.pdf}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Free Books}
\begin{itemize}
\item {\bf Bayesian Reasoning and Machine Learning}
      David Barber (2014)
      \url{http://www.cs.ucl.ac.uk/staff/d.barber/brml/}
\item {\bf Gaussian Processes for Machine Learning}
      Carl Edward Rasmussen and Christopher K. I. Williams (2006)
      \url{http://www.gaussianprocess.org/gpml/chapters/}
\item {\bf Information Theory, Inference, and Learning Algorithms}
      David J.C. MacKay (2003)
      \url{http://www.inference.phy.cam.ac.uk/itila/book.html}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Web sites}
\begin{itemize}
\item {\bf Kernel Machines} \url{http://www.kernel-machines.org/}
\item {\bf The Gaussian Processes Web Site} includes links to software. \url{http://www.gaussianprocess.org/}
\item {\bf SVM - Support Vector Machines} includes links to software. \url{http://www.support-vector-machines.org/}
\item {\bf Pascal Video Lectures}  \url{http://videolectures.net/pascal}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{MATLAB tools}
\begin{itemize}
\item \textbf{Spider} Object orientated environment for machine learning in MATLAB.
\item \textbf{GPML} Gaussian processes for supervised learning. % (\url{http://www.gaussianprocess.org/gpml/code/matlab/doc/}).
\item \textbf{Pronto} MATLAB ML tbx for neuroimaging. GUI. Implements many ML concepts. Continuity with SPM.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Python tools}
\begin{itemize}
\item \textbf{Scikit-learn} Generic ML in Python. Complete,
  high-quality, well-documented, reference implementations.
\item \textbf{Nilearn} Python interface to Scikit-learn for
  Neuroimaging. Easy-to-use/install. Good viz.
\item \textbf{Pymvpa} Python tool for ML. Advanced stuff
  (Pipelines, Hyperalignment).
\end{itemize}
\end{frame}

